Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints\thanks{This research was supported by the Russian Science Foundation, project No. 16-11-10150.}

### 2020-02-01 2019/NUMTA_Barkalov/SoftComputing/article.tex
Decreased the font in 4, 5

	Along with the exact solution $y^\ast$ of the problem (\ref{problem}), we will consider also the $\varepsilon$-reserved solution $y_{\epsilon}$, for which 
\begin{align}\label{epsilon_reserved_solution}
	\varphi(y_{\epsilon}) & = \nonumber \\
	& \min{\left\{\varphi(y):y \in D, g_j(y)\leq -{\epsilon}_j, 1 \leq j \leq m\right\}},
\end{align}
and the set of solutions $Y_{\epsilon}$, which are not worse than the $\varepsilon$-reserved solution in the objective function value, i.e.
\begin{align}\label{Y_epsilon}
	Y_{\epsilon} & = \nonumber \\
	& \left\{ y \in D, \; g_j(y) \leq 0, \; 1 \leq j \leq m, \; \varphi(y) \leq \varphi(y_{\epsilon}) \right\}.
\end{align}
Fig. \ref{fig:eps_reserved_solution} illustrates the concepts introduced.

>>>>

	Along with the exact solution $y^\ast$ of the problem (\ref{problem}), we will consider also the $\varepsilon$-reserved solution $y_{\epsilon}$, for which 
\small
\begin{align}\label{epsilon_reserved_solution}
	\varphi(y_{\epsilon}) = \min{\left\{\varphi(y):y \in D, g_j(y)\leq -{\epsilon}_j, 1 \leq j \leq m\right\}},
\end{align}
\normalsize
and the set of solutions $Y_{\epsilon}$, which are not worse than the $\varepsilon$-reserved solution in the objective function value, i.e.
\small
\begin{align}\label{Y_epsilon}
	Y_{\epsilon} = \left\{ y \in D, \; g_j(y) \leq 0, \; 1 \leq j \leq m, \; \varphi(y) \leq \varphi(y_{\epsilon}) \right\}.
\end{align}
\normalsize
Fig. \ref{fig:eps_reserved_solution} illustrates the concepts introduced.
